Supplementary Material for ``Evaluating infectious disease forecasts with allocation scoring rules''

### 2023-12-21 alloscore_manuscript/supplement_short.tex
reword dfq Bayes sr

The set $\mathcal{P}_{\mathrm{dfq}}$ with map $M(G_{\theta}):= x^{G_{\theta}}$ is surjective onto the action set of allocations
under any constraint $K$ since they can be specified as quantiles for distributions in $\mathcal{P}_{\mathrm{dfq}}$.  Therefore
the \verb`distfromq` ``reparametrized'' allocation scoring rule coincides with the AS itself.

>>>>

Identifying $G_{\theta}\in \mathcal{P}_{\mathrm{dfq}}$ with its quantile parameters $\theta$, the map $M(\theta):= x^{\theta}$  
is surjective onto the action set of allocations under any constraint $K$ since they can be specified as quantiles for 
distributions in $\mathcal{P}_{\mathrm{dfq}}$.  Therefore
the \verb`distfromq` ``reparametrized'' allocation scoring rule 
$S_{A, \mathrm{dfq}}(F,y):= s_{\mathrm{dfq}}(\theta^F,y) = s_A(x^{\theta^F},y)$ coincides with the AS $S_A(F,y)$ itself.
